ESRC SDAI Application

### 2019-06-24 case_for_support.tex
Anna update

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In our first research project, we will be investigating three main research questions. First, we will use the CSEW and WMP datasets to identify the demographic and socio-economic characteristics of victims of domestic abuse, and the WMP to characterise perpetrators of domestic abuse cases reported to the police. Second, we will estimate the true extent of domestic abuse victimisation. Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the extent of domestic abuse victimisation and the subsequent societal costs. We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related). Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide. Finally, we will estimate the extent of police mis-recording of domestic abuse. Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm. By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.

@@

\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation. Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, frequency of drug and alcohol use. Using this wide range of individual-level information, we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW. We are particularly interested in the association between experiences of domestic abuse and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.

Second, we can validate some of these findings using the WMP data. This dataset contains information about the sex and age of victims. We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW\textit{(we were initially talking about using victims of burglary, but maybe this is better?)}. We can complement this analysis with data on the offender's sex  and age to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.

>>>>

 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In our first research project, we will be investigating three main research questions. First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data. Second, we will estimate the true extent of domestic abuse victimisation. Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the extent of domestic abuse victimisation and the subsequent societal costs. We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related). Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide. Finally, we will estimate the extent of police mis-recording of domestic abuse. Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm. By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.

@@

\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors predicting domestic abuse victimisation. Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse ever suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use. Using this wide range of individual-level information, we will evaluate the importance of each of these variables in predicting the likelihood of domestic abuse victimisation. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance? this way we could also look at interactions? does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW. We are particularly interested in the association between experiences of domestic abuse, number of children and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.

Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the victim reported the domestic abuse to the police. The WMP contains information about the sex and age of victims. We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW \textit{(we were initially talking about using victims of burglary, but maybe this is better?)}. We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.
